A Decision Procedure for (Co)datatypes in SMT Solvers

### 2015-02-24 tex/body.tex
more

For each goal in each theory, Sledgehammer was invoked to select up to
256~lemmas, which were monomorphized and translated to SMT-LIB~2
along with the goal \cite{blanchette-et-al-2013-smt}. The resulting problem was
given to the development version of CVC4 and to Z3 4.3.2, each running for up to 60
seconds on the StarExec cluster \cite{stump-et-al-2014-starexec}.
%TODO: Keep or not? Problems not involving (co)datatypes were filtered out.
Due to the lack of machinery for reconstructing inferences about (co)datatypes
in Isabelle, the solvers are trusted as oracles in these experiments. Z3
is included for comparison.

>>>>

{\looseness=-1
For each goal in each theory, Sledgehammer was invoked to select up to
256~lemmas, which were monomorphized and translated to SMT-LIB~2
along with the goal \cite{blanchette-et-al-2013-smt}. The resulting problem was
given to the development version of CVC4 and to Z3 4.3.2 for comparison, each
running for up to 60 seconds on the StarExec cluster
\cite{stump-et-al-2014-starexec}.
%Problems not involving (co)datatypes were left out.
Due to the lack of machinery for reconstructing inferences about (co)datatypes
in Isabelle, the solvers are trusted as oracles. % in these experiments.
%Z3 is included for comparison.
